
---
output:
  pdf_document:
    includes:
      in_header: mystyle.sty
tables: yes
graphics: yes
latex_engine: xelatex
highlight: zenburn
toc: no
fig_width: 4
fig_height: 2.6
header-includes:
     - \usepackage{longtable}

---

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, error= FALSE }
# No scientific notation
options(scipen=999)

#####
# PACKAGES
#####
library(ggmap)
library(dplyr)
library(xtable)
library(ggplot2)
library(ggthemes)
library(png)
library(grid)
library(extrafont)
library(raster)
library(rgdal)
library(tidyr)
library(gridExtra)
library(maps)
loadfonts(device = 'postscript', quiet = TRUE)

# BASIC KNITR OPTIONS
library(knitr)
opts_chunk$set(comment = NA, echo = FALSE, warning = FALSE, message = FALSE)
options(xtable.comment = FALSE)
```

```{r, echo = FALSE, warning = FALSE, message = FALSE, comment = NA, error= FALSE}
root_dir <- "/home/joebrew/Documents/data_baby/"
```

```{r}
# SOURCE HELPERS
source('helpers/my_theme.R')
```

# Conception  

## It all starts with sex  

You aren’t the only ones doing it, you know.  Of the 7 billion humans on earth, 4.6 billion are sexually active, and more than 3 billion have had sex in the last week.  The average adult is getting it on about 1.4 times per week.  

```{r}
suppressWarnings(source(paste0(root_dir, 'frequency_sex/code/icpsr.R')))
```


```{r}
suppressWarnings(source(paste0(root_dir, 'icpsr/code/icpsr.R')))
```

```{r, fig.width= 4, fig.height = 3, fig.align = 'center'}
# AGE OF FIRST VAGINAL INTERCOURSE
age_first_vi()
```

The average duration of intercourse (not counting pre-sex foreplay or post-sex cuddling/remorse) is 3 minutes and 12 seconds. My condolences, ladies.  This means that when you and honey are rocking the bed, you’ll be joined by 1.2 million other sweaty, fleshy, grunty earthlings all doing the same thing, at the exact same time.  Stage fright, anyone?

Of course sex doesn’t necessarily mean conception.  In fact, it very rarely does.  The modern American woman will have sex about 3,450 times in her life, resulting in 4.1 pregnancies and 2.3 children.  Most of the pregnancies not ending in childbirth will end spontaneously in the first few weeks after conception - and the woman most often will not be aware.  The number of medical abortions per year - approximately 48,000 - constitutes approximately 1.5% of all (known) pregnancies in the US.  This number 


